The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-03-13 analysis/paper/paper.qmd
Only extract text from PDF if extracted text is missing

```{r}
#| label: extract-pdf-text
#| echo: false

# Extract text from PDFs
# On the first run, this function might take extra time as a Python environment needs to be set up

emu_theses$text <- convert_pdf_text(pdf_paths)
```

@@

Distinctive features of the program:  
- as a postmaster, it only accepted applicants with a prior MSc degree and experience in practice
- provides a bridge towards PhD-level research
- all students had an exchange semester at one of the other three program universities

@@

<!-- ```{r} -->

<!-- # Which theses contain "fabric" in the top 20 most frequently used words? -->

<!-- emu_theses_top_20 %>%  -->

<!--   filter(word == "fabric") -->

<!-- emu_theses_top_20 %>% -->

<!--   slice(1:40) %>%  -->

<!--   ggplot(aes(x = reorder(word, n), y = n, fill = title)) + -->

<!--   geom_col() + -->

<!--   xlab(NULL) + -->

<!--   coord_flip() + -->

<!--   labs(y = "Count", -->

<!--        x = "Unique words", -->

<!--        title = "Count of unique words found in thesis", -->

<!--        subtitle = "Stop words were removed from the list") + -->

<!--   facet_wrap( ~ title, scales = "free", ncol = 2) -->

<!-- ``` -->

>>>>

```{r}
#| label: extract-pdf-text
#| echo: false
#| cache: true

data_path <- here("analysis", "data", "derived_data", "emu_theses_with_text.csv")

if (!file.exists(data_path)) {
  # On the first run, this function might take extra time as a Python environment needs to be set up
  emu_theses$text <- convert_pdf_text(pdf_paths)
  write_csv(emu_theses, data_path)
} else {
  emu_theses <- read_csv(data_path)
}

```

@@

@@

<!-- ```{r} -->
<!-- # Which theses contain "fabric" in the top 20 most frequently used words? -->
<!-- emu_theses_top_20 %>%  -->
<!--   filter(word == "fabric") -->

<!-- emu_theses_top_20 %>% -->
<!--   slice(1:40) %>%  -->
<!--   ggplot(aes(x = reorder(word, n), y = n, fill = title)) + -->
<!--   geom_col() + -->
<!--   xlab(NULL) + -->
<!--   coord_flip() + -->
<!--   labs(y = "Count", -->
<!--        x = "Unique words", -->
<!--        title = "Count of unique words found in thesis", -->
<!--        subtitle = "Stop words were removed from the list") + -->
<!--   facet_wrap( ~ title, scales = "free", ncol = 2) -->
<!-- ``` -->
